We kind of need a title

### 2020-02-28 methodology.tex
Finished methodology
Removed thing about quoting responses

    This is the methodology for IRB-20-0417, titled "Survey on the Role of Artificial Intelligence in Healthcare". It is a survey aiming to gauge the general opinion, expectations, and fears regarding medical AI within the nursing student community. We aim to distribute it at nearby nursing schools.

@@

    We may chose to directly quote portions of free text responses, however they will not be paired with other responses from that individual and will be anonymized in order to limit potential risk to participants. While we do not anticipate that the resulting data corpus will contain anything that may risk harm to participants, we intend to do our best to eliminate any and all risk.

>>>>

    This is the methodology for IRB-20-0598, titled "Survey on the Role of Artificial Intelligence in Healthcare". It is a survey aiming to gauge the general opinion, expectations, and fears regarding medical AI within the nursing student community. We aim to distribute it at nearby nursing schools.

@@
